Computer Science House Constitution

### 2019-02-18 articles.tex
New Section

\asection{Resignations}
An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairman.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time. 
Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place. 
If necessary, the Chairman may chair a vote during before an election deadline to delay the election by a specified time with a specific reason presented at house meeting; the vote will qualify as a fifty percent vote. See fifty percent vote \ref{Fifty Percent}.

@@

>>>>

\asection{Resignations}
An Executive Board Member may resign their position by submitting in writing the reason for resignation to the House Chairman.
The resignation will be read at the following House Meeting and become effective at that time.
The office will become vacant and the selection process for a new member as described in section \ref{Appointment of an Interim Director} will begin at that time. 
Following a resignation, an election must be held for the position vacated within two weeks from when the resignation took place.

@@

\asection{Delaying Election}
If necessary, the Chairman may chair a vote before an election deadline at house meeting to delay the election by a specified time with a specific reason presented at house meeting; the vote will qualify as a fifty percent vote. See fifty percent vote \ref{Fifty Percent}. 
If the vote fails, the election deadline already established will stay in effect.
